\begin{thebibliography}{99}
\bibitem{KB} Kurt Bryan. {\it Elementary Inversion of the Laplace Transform} https://www.rose-hulman.edu/~bryan/invlap.pdf

\bibitem{OV} G.E. Parker, J.S. Sochacki et al., An Overview of the Modied Picard
Method, http://educ.jmu.edu/sochacjs/expository.pdf

\bibitem{CL} E.A. Coddington and N. Levinson, Theory of Ordinary Differential Equations, McGraw-Hill, New York, 1955

\bibitem{PS} G.E. Parker and J.S. Sochacki, Implementing the Picard Iteration, Neural, Parallel and Scientic Computations, 4 (1996) 1, pp. 97-112.

\bibitem{CPSW} D.C. Carothers, G.E. Parker, J.S. Sochacki and P. G. Warne, Some
Properties of Solutions to Polynomial Systems of Equations, Elec. Jour. of Diff. Eqn.,
2005 (2005) 40, pp. 1-17.

\bibitem{EX} P. G. Warne, D. A. P. Warne, J. S. Sochacki, G. E. Parker and D. C.
Carothers, Explicit A-Priori Error Bounds and Adaptive Error Control for Approx-
imation of Nonlinear Initial Value Differential Systems, Comput. Math. Appl., 52
(2006), pp. 1695-1710.

\bibitem{PSM} Kurt Bryan. {\it Elementary Inversion of the Laplace Transform} https://www.rose-hulman.edu/~bryan/invlap.pdf

\bibitem{NORMAL} Kurt Bryan. {\it Elementary Inversion of the Laplace Transform} https://www.rose-hulman.edu/~bryan/invlap.pdf

\bibitem{SETTLE} Kurt Bryan. {\it Elementary Inversion of the Laplace Transform} https://www.rose-hulman.edu/~bryan/invlap.pdf

\bibitem{BE} Kurt Bryan. {\it Elementary Inversion of the Laplace Transform} https://www.rose-hulman.edu/~bryan/invlap.pdf

\end{thebibliography}